### 2021-03-12 results/draft.tex
small changes

\ \ \ \ \ \ \ \ \ \ 
Integrated species distribution models (IDMs) are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
% As alternative approach to over come the spatial uncertainty of eDNA, statistical modeling approach should be a useful approach.
%The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al. 2020; Miller et al. 2019).
%The model use the different type of data with strengths and weaknesses, such as scientific survey data (high quality but not abundant) and opportunistic citizen data (low quality but abundant) , and combine in a single model (Isaac et al. 2020; Miller et al. 2019).
The models combine the different type of data with strengths and weaknesses in a single model. For example, the model can use both scientific survey data, which is high quality but less abundant due to restriction of cost, and citizen data, which is widely collected and abundant but may be low quality due to not using consistent field methods in a model.
%scientific survey data are high quality but less abundant due to restriction of spatially costly while opportunistic data such as citizen data are widely collected and abundant but may be low quality due to not using consistent field methods.
Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when using single data (Pacifici et al. 2017; Miller et al. 2019). 
Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, as well as treating environmental factors as covariance in the model, then the spatial uncertainty of eDNA should be reduced and the model inference should be improved (Fig. 1).
%Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, then the model inference of the spatial distribution should be reduced about spatial uncertainty of eDNA and should be improved.   
%したがって，統合モデルにより『生物がその場所に生息する』という情報をeDNAに加えることで，eDNA
%したがって，eDNAデータと新たなデータ（『生物がその場所に生息する』という情報を持つ）を使って統合モデルを構築すれば，eDNAデータに対する空間的な不確実性は減少し，eDNAから推定される空間分布の精度は上昇することが期待される．

>>>>

\ \ \ \ \ \ \ \ \ \ 
Integrated species distribution models (IDMs) are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
% As alternative approach to over come the spatial uncertainty of eDNA, statistical modeling approach should be a useful approach.
%The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data which is widely collected and abundant, and combine in a single model (Isaac et al. 2020; Miller et al. 2019).
%The model use the different type of data with strengths and weaknesses, such as scientific survey data (high quality but not abundant) and opportunistic citizen data (low quality but abundant) , and combine in a single model (Isaac et al. 2020; Miller et al. 2019).
The models combine the different type of data with strengths and weaknesses in a single model. For example, the model can use both scientific survey data, which is high quality but less abundant due to restriction of cost, and citizen data, which is widely collected and abundant but may be low quality due to not using consistent field methods in a model.
%scientific survey data are high quality but less abundant due to restriction of spatially costly while opportunistic data such as citizen data are widely collected and abundant but may be low quality due to not using consistent field methods.
Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when using single data (Pacifici et al. 2017; Miller et al. 2019). 
Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, as well as environmental factors as covariance in the model, then the inference from the model should represent the reduction of the spatial uncertainty of eDNA and improvement (Fig. 1).
%reduction of the spatial uncertainty of eDNA and improvement of the inference of spatial distribution from eDNA should be expected (Fig. 1).
%the spatial uncertainty of eDNA should be reduced and the model inference should be improved (Fig. 1).
%Hence, if we develop a IDM that uses not only eDNA data but also the second data which contains the information that species exists at a location, then the model inference of the spatial distribution should be reduced about spatial uncertainty of eDNA and should be improved.   
%したがって，統合モデルにより『生物がその場所に生息する』という情報をeDNAに加えることで，eDNA
%したがって，eDNAデータと新たなデータ（『生物がその場所に生息する』という情報を持つ）を使って統合モデルを構築すれば，eDNAデータに対する空間的な不確実性は減少し，eDNAから推定される空間分布の精度は上昇することが期待される．
